---
title: "Visualising_Financial_Statements"
author: "Anshul Singhal"
date: "9/19/2021"
output: github_document

---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

##Loading the Packages which are required
```{r include = FALSE}
library(dplyr)
require(data.table)
library(haven)
library(zeallot)
library(lubridate)
library(plotly)
library(openxlsx)
library(readxl)
library(zoo)
library(scales)
library(geckor)
library(fredr)
library(tidyquant)
library(tidyr)
library(naniar)
library(tidyverse)
fredr_set_key("669c24e3e2c8136b6db6b3c978104993")
```

#Relevant Functions used in the Code
```{r}
"Correlation Heatmap Function"
get_heatmap = function(dat,columns,col_name){
  corr = round(x = cor(dat[columns],use = "complete.obs"), digits = 2)
  melted_corr = reshape2::melt(corr)
  heatplot = ggplot(data = melted_corr, aes(x=Var1, y=Var2, fill = value)) +
    geom_tile(color = "white")+
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
    midpoint = 0, limit = c(-1,1), space = "Lab", 
    name="Pearson\nCorrelation") +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5),axis.text.x = element_text(angle=45, hjust=1)) +
    labs(title = paste0("Correlation Heatmap for ",col_name))+
    coord_fixed()
  ggplotly(heatplot)
}

"Multiple Line chart Function to draw line chart across time with the Macro economic variables"
#Plot the multiple line charts for the securities along with the macro-economic indicators
plot_multiple_line_chart = function(dat1, title_type,y1_type,macro_flag = 0) {
  if(macro_flag == 0){
    cols_taken = ncol(dat1)
  }else{
    cols_taken = ncol(dat1)-1
  }
  plot_y <- dat1 %>% plot_ly()
  for(i in c(2:ncol(dat1))) {
    if (i <= cols_taken) {
      x = plot_y %>% add_trace(x = ~fyear, y=dat1[[i]],  mode="lines" ,type = 'scatter', name=colnames(dat1)[i], yaxis='y1')
    } else if(macro_flag != 0){
      x = plot_y %>% add_trace(x = ~fyear, y=dat1[[i]], mode="lines", type = 'scatter', name=colnames(dat1)[i], yaxis='y2') 
    }
    plot_y = x
  }
  if(macro_flag != 0)
  {
      plot_y %>% 
      layout(title = paste0(title_type,"(LHS) vs Macro economic variable (RHS)"),
         barmode   = 'relative', 
         xaxis     = list(title=''),
         margin    = list(l = 75, r = 75, b = 50, t = 50, pad = 4),
         xaxis     = list(title = ""),
         yaxis     = list(side = 'left', 
                       title = y1_type, 
                       showgrid = FALSE, 
                       zeroline = TRUE, 
                       color = 'steelblue'),
         yaxis2    = list(side = 'right', 
                       overlaying = "y", 
                       title = colnames(dat1)[ncol(dat1)], 
                       showgrid = TRUE, 
                       zeroline = FALSE,
                       # ticksuffix = "%", 
                       color = "#ffa500"),
         legend = list(traceorder = 'reversed',orientation = "h"))
  }
  else{
    plot_y %>% 
    layout(title = paste0(title_type," Data"),
       barmode   = 'relative', 
       xaxis     = list(title=''),
       margin    = list(l = 75, r = 75, b = 50, t = 50, pad = 4),
       xaxis     = list(title = ""),
       yaxis     = list(side = 'left', 
                       title = y1_type, 
                       showgrid = FALSE, 
                       zeroline = TRUE, 
                       color = 'steelblue'),
       legend = list(traceorder = 'reversed',orientation = "h"))
  }
}

"Box-Plot Function"
get_boxplot = function(in_data,variable_name,full_plot){
  box_plot_data = in_data%>%
    select(fyear,variable_name)
  names(box_plot_data)[2] = "value"
  
  if(full_plot == 1)
  {
    p = ggplot(box_plot_data, aes(x=as.factor(fyear), y=value)) +
      geom_boxplot(fill='red', color="dark green")+
      theme_classic()+
      coord_cartesian(y = c(-5000,5000))+
      labs(x = "Year", y = variable_name)
  }else{
      p = ggplot(box_plot_data, aes(x=as.factor(fyear), y=value)) +
        geom_boxplot(fill='red', color="dark green")+
        theme_classic()+
        coord_cartesian(y = c(-15,15))+
        labs(x = "Year", y = variable_name)
  }
  return (p)
}

"Box-Plots for all variable(Loop)"
plot_all_boxplots = function(in_data,full = 0){
  col_names = colnames(in_data)[2:ncol(in_data)]
  for (i in 1:length(col_names)){
    print(get_boxplot(in_data,col_names[i],full))
  }
}

"Descriptive Stats Function : count, mean, p25, p50, p75, std, max, min"
stats = function(dat){
count_group = dat %>%
  group_by(BK_START)%>%
  summarise(across(everything(),funs(sum(!is.na(.))),.names = "count_{.col}"))
mean_group = dat %>%
  group_by(BK_START)%>%
  summarise(across(everything(), mean,na.rm = TRUE,.names = "mean_{.col}"))
p25_group = dat %>%
  group_by(BK_START)%>%
  summarise(across(everything(), quantile,probs = c(0.25),na.rm = TRUE,.names = "p25_{.col}"))
p50_group = dat %>%
  group_by(BK_START)%>%
  summarise(across(everything(), quantile,probs = c(0.5),na.rm = TRUE,.names = "p50_{.col}"))
p75_group = dat %>%
  group_by(BK_START)%>%
  summarise(across(everything(), quantile,probs = c(0.75),na.rm = TRUE,.names = "p75_{.col}"))
std_group = dat %>%
  group_by(BK_START)%>%
  summarise(across(everything(), sd,na.rm = TRUE,.names = "std_{.col}"))
max_group = dat %>%
  group_by(BK_START)%>%
  summarise(across(everything(), max,na.rm = TRUE,.names = "max_{.col}"))
min_group = dat %>%
  group_by(BK_START)%>%
  summarise(across(everything(), min,na.rm = TRUE,.names = "min_{.col}"))
 return (list(count_group,mean_group, p25_group,p50_group, p75_group, std_group,max_group,min_group))
}

```
##Reading the data
```{r}
"Selecting the variables to read from the SAS dataset (Combined the variables from excel sheet)"
#Reading the variables extracted from the tables
variables = read.csv("Variable_Names.csv")
variables$lower = tolower(variables$Variable_Name)
variable_list = unique(variables$lower)
```

##Dateset Manipulation
```{r}
"Importing the dataset with only selected variables"
# path = "Q:/Data-ReadOnly/COMP/"
# subset_data = read_sas(paste0(path,"funda.sas7bdat"),n_max = 1000)
col_list = c("gvkey","fyear","indfmt","tic","conm","scf","compst","sich",variable_list)
subset_data = read_sas("funda.sas7bdat",col_select = col_list)

"Filtering the dataset based on the requirements"
#Taking only the relevant data and dropping rows corresponding to the column Total Assets which have NA values. No point of taking the other values in the row (variables) if we don't have Total assets(at) data
subset_data = subset_data%>%
  filter(compst != "AB",!(sich %in% 4900:4999),!(sich %in% 6000:6999),!(scf %in% (4:6)))%>%
  select(-c(compst,sich))%>%
  drop_na(at,scf)

```

##GDP Defaltor loaded
```{r}
"For every year multiplier is calculated based on the base year 1992(67.89 value of the GDP Defaltor)"
gdp_deflator <- 
   "GDPDEF" %>% 
  tq_get(get = "economic.data", from = "1971-01-01") %>% 
  select(fyear = date, index  =  price) %>% 
  mutate(fyear = as.numeric(year(fyear)))%>%
  group_by(fyear)%>%
  slice(n())%>%
  mutate(multiplier = 67.889/index)
```

##Subset Data after 1992 dollar terms
```{r}
#Final data which can be used for further analysis
year_list = c(1971,1974,1979,1984,1988,1990,1995,1999,2002,2005,2008,2011,2014,2017,2020)
selected_data = subset_data%>%
  filter(fyear %in% year_list)%>%
  merge(gdp_deflator[c("fyear","multiplier")],by = "fyear")

selected_data[,7:(ncol(selected_data)-1)] = selected_data[,7:(ncol(selected_data)-1)]*unlist(selected_data["multiplier"])
selected_data = selected_data%>%
  select(-multiplier)
```

##Desciptive Stats and Box Plots of tables
```{r}
"Modifying the tables and recording the original NA values, calculating the descriptive stats and box plots for all variables in the table"
#Taking only those rows for a year of a company where total assets are not zero
selected_data = selected_data[selected_data["at"]!=0,]
selected_data = arrange(selected_data,gvkey,fyear)

na_values = is.na(selected_data)
#Replacing remaining NA values with zero so, as to compute the compound variables
selected_data[is.na(selected_data)] = 0

Modified_Data = selected_data %>%
  mutate(non_operating_income_special_items = nopi+spi,
         other_funds_from_operation = xidoc+txdc+esubc+sppiv+fopo,
         short_term_investment = ivstch+ivaco)

#Copying the NA's back to the original data so that we don't include the balance sheet variables in the calculation of mean etc.
Modified_Data_NA = copy(Modified_Data)
for (i in (1:ncol(na_values))){
  if(any(na_values[,i])){
    Modified_Data_NA[,i] = replace(as.vector(unlist(Modified_Data_NA[,i])), na_values[,i] == TRUE, NA)
  }
}

balance_sheet_variables = c("ch","ivst","rect","invt","aco","act","ppent","ivaeq","ivao","intan","ao","at",
                           "dlc","ap","txp","lco","lct","dltt","lo","txditc","mib","lt","pstk","ceq","teq",
                           "at")
income_statement_variables = c("sale","cogs","xsga","oibdp","dp","oiadp","xint","non_operating_income_special_items","pi","txt","mii","ib","dvp","cstke","xido","ni")

cash_flow_statement_variables = c("ibc","dpc","other_funds_from_operation","fopt","recch","invch","apalch","txach","aoloch","oancf","ivch","siv","capx","sppe","aqc","short_term_investment","ivncf","sstk","prstkc","dv","dltis","dltr","dlcch","fiao","fincf","exre","chech","fsrco","fuseo","wcapc")

Balance_Sheet_Data = Modified_Data_NA%>%
  select(c(fyear,balance_sheet_variables))%>%
  group_by(fyear)%>%
  mutate(across(everything(),.fns = ~./at))

Income_Statement_Data = Modified_Data_NA%>%
  select(c(fyear,income_statement_variables,at))%>%
  group_by(fyear)%>%
  mutate(across(everything(),.fns = ~./at))%>%
  select(-at)

Cash_Flow_Data = Modified_Data_NA%>%
  select(c(fyear,cash_flow_statement_variables,at))%>%
  group_by(fyear)%>%
  mutate(across(everything(),.fns = ~./at))%>%
  select(-at)

#Descriptive Stats for the tables
c(count_balance_sheet_data,mean_balance_sheet_data,p25_balance_sheet_data,p50_balance_sheet_data, p75_balance_sheet_data, std_balance_sheet_data,max_balance_sheet_data,min_balance_sheet_data)%<-%stats(Balance_Sheet_Data)

c(count_income_statement_data,mean_income_statement_data,p25_income_statement_data,p50_income_statement_data, p75_income_statement_data, std_income_statement_data,max_income_statement_data,min_income_statement_data)%<-%stats(Income_Statement_Data)


c(count_cash_flow_data,mean_cash_flow_data,p25_cash_flow_data,p50_cash_flow_data, p75_cash_flow_data, std_cash_flow_data,max_cash_flow_data,min_cash_flow_data)%<-%stats(Cash_Flow_Data)
#Box plots of all variables in the three tables(Balance Sheet, Income Statement, Cash Flow Statement)
# pdf("All_plots.pdf")
plot_all_boxplots(Balance_Sheet_Data)
plot_all_boxplots(Income_Statement_Data)
plot_all_boxplots(Cash_Flow_Data)


```

##Table 10(Correlation Features from Table 9)
```{r}

#Adding new features to the Data
Modified_Data = Modified_Data %>% 
  mutate(cash_dividends_net_assets =if_else((at-lct) !=0, dv/(at-lct),NA_real_),
         investment_net_assets = if_else((at-lct)!=0, if_else(scf > 0 & scf <= 3,(capx+ivch+aqc+fuseo-sppe-siv),if_else(scf == 7,(capx+ivch+aqc-sppe-siv-ivstch-ivaco),NA_real_))/(at-lct),NA_real_),
        change_working_capital_net_assets = if_else((at-lct)!=0,if_else(scf == 1,(wcapc+chech+dlcch),if_else(scf == 2 & scf == 3,(-wcapc+chech-dlcch),if_else(scf == 7,(-recch-invch-apalch-txach-aoloch+chech-fiao-dlcch),NA_real_)))/(at-lct),NA_real_),
        internal_cash_flow_net_assets = if_else((at-lct)!=0,if_else(scf > 0 & scf <= 3,(ibc+xidoc+dpc+txdc+ esubc+sppiv+fopo+fsrco),if_else(scf == 7,(ibc+xidoc+dpc+txdc+esubc+sppiv+fopo+exre),NA_real_))/(at-lct),NA_real_),
        financing_deficit_net_assets = cash_dividends_net_assets+investment_net_assets+change_working_capital_net_assets-internal_cash_flow_net_assets,
        gross_lt_debt_issued_net_assets = if_else((at-lct)!=0,dltis/(at-lct),NA_real_),
        net_lt_debt_issued_net_assets = if_else((at-lct)!=0,(dltis - dltr)/((at-lct)),NA_real_),
        net_equity_issued_net_assets = if_else((at-lct)!=0,(sstk - prstkc)/((at-lct)),NA_real_),
        net_external_financing_net_assets = if_else((at-lct)!=0,(net_lt_debt_issued_net_assets+net_equity_issued_net_assets),NA_real_),
        total_debt_book_cap = if_else((at-lt)!=0,(dlc+dltt)/(at-lt),NA_real_),
        tangibility = if_else(at!= 0,ppent/at,NA_real_),
        market_book_assets = mkvalt/at,
        log_sales = if_else(sale != 0,log(sale),NA_real_),
        profitability = ni/at)

#Descriptive stats for key variables
c(count_key_variables_t9,mean_key_variables_t9,p25_key_variables_t9,p50_key_variables_t9, p75_key_variables_t9, std_key_variables_t9,max_key_variables_t9,min_key_variables_t9)%<-%stats(Modified_Data[c(1,90:length(colnames(Modified_Data)))])
#Heatmap for the above mean key variables over time
get_heatmap(mean_key_variables_t9,colnames(mean_key_variables_t9)[2:length(colnames(mean_key_variables_t9))],"Analysis")

```

##Financial Ratios Table (Additional Table)
```{r}
"Financial Ratios"
#Here we take all the data over all the years not just the selected list of years as taken previously as when we take lag then it should calculate over previous year which will not happen if we discontinuity in the data


#Performing the similar operations of dropping AT where values are 0 and sorting the data by gvkey and fyear and later subsetting the data for only selected years
all_data = subset_data%>%
  merge(gdp_deflator[c("fyear","multiplier")],by = "fyear")

all_data[,7:(ncol(all_data)-1)] = all_data[,7:(ncol(all_data)-1)]*unlist(all_data["multiplier"])

all_data = all_data[all_data["at"]!=0,]
all_data = all_data%>%
  select(-multiplier)

all_data[is.na(all_data)] = 0

Financial_Ratios_Data = all_data %>% 
  group_by(gvkey,fyear)%>% 
  mutate(current_ratio = if_else(lct!=0, act/lct,NA_real_),
        quick_ratio = if_else(lct!=0,(che+rect)/lct,NA_real_),
        debt_equity_ratio = if_else(teq!=0,lt/teq,NA_real_),
        dso = if_else(sale!=0,((rect + if_else(is.na(lag(rect)),0,lag(rect)))*0.5/sale)*365,NA_real_),
        dio = if_else(cogs!=0,((invt + if_else(is.na(lag(invt)),0,lag(invt)))*0.5/cogs)*365,NA_real_),
        dpo = if_else(cogs!=0,((ap + if_else(is.na(lag(ap)),0,lag(ap)))*0.5/cogs)*365,NA_real_),
        cash_conversion_cycle = dio + dso - dpo,
        total_asset_turnover = if_else((at + if_else(is.na(lag(at)),0,lag(at)))!=0,sale/((at + if_else(is.na(lag(at)),0,lag(at)))*0.5),NA_real_),
        inventory_turnover = if_else((invt + if_else(is.na(lag(invt)),0,lag(invt)))!=0,cogs/((invt + if_else(is.na(lag(invt)),0,lag(invt)))*0.5),NA_real_),
        receivable_turnover = if_else((rect + if_else(is.na(lag(rect)),0,lag(rect)))!=0,sale/((rect + if_else(is.na(lag(rect)),0,lag(rect)))*0.5),NA_real_),
        interest_burden = if_else(oiadp!=0,(oiadp-xint)/oiadp,NA_real_),
        interest_coverage = if_else(xint!=0,oiadp/xint,NA_real_),
        leverage = if_else(teq!=0,at/teq,NA_real_),
        roa = if_else((at + if_else(is.na(lag(at)),0,lag(at)))!=0,oiadp/((at + if_else(is.na(lag(at)),0,lag(at)))*0.5),NA_real_),
        roe = if_else((teq + if_else(is.na(lag(teq)),0,lag(teq)))!=0,ni/((at + if_else(is.na(lag(teq)),0,lag(teq)))*0.5),NA_real_),
        ros = if_else(sale!=0,oiadp/sale,NA_real_))%>% 
  ungroup()%>%
  filter(fyear %in% year_list)

liquidity_solvency_ratios = c("current_ratio","quick_ratio","debt_equity_ratio")
activity = c("dso","dio","dpo","cash_conversion_cycle")
asset_utilization = c("total_asset_turnover","inventory_turnover","receivable_turnover")
leverage_ratio = c("interest_burden","interest_coverage","leverage")
profitability_ratio = c("roa","roe","ros")

#calculating the different ratios for each of the tabs in the excel file(  additional table)
Liquidity_Solvency = Financial_Ratios_Data%>%
  select(c(fyear,liquidity_solvency_ratios))

Activity = Financial_Ratios_Data%>%
  select(c(fyear,activity))

Asset_Utilization = Financial_Ratios_Data%>%
  select(c(fyear,asset_utilization))

Leverage = Financial_Ratios_Data%>%
  select(c(fyear,leverage_ratio))

Profitability = Financial_Ratios_Data%>%
  select(c(fyear,profitability_ratio))

#Calcualting the descriptive stats for all of the above datasets
c(count_liquidity_solvency_data,mean_liquidity_solvency_data,p25_liquidity_solvency_data,p50_liquidity_solvency_data, p75_liquidity_solvency_data, std_liquidity_solvency_data,max_liquidity_solvency_data,min_liquidity_solvency_data)%<-%stats(Liquidity_Solvency)

c(count_activity,mean_activity,p25_activity,p50_activity, p75_activity, std_activity,max_activity,min_activity)%<-%stats(Activity)

c(count_asset_utiltization,mean_asset_utiltization,p25_asset_utiltization,p50_asset_utiltization, p75_asset_utiltization, std_asset_utiltization,max_asset_utiltization,min_asset_utiltization)%<-%stats(Asset_Utilization)

c(count_leverage,mean_leverage,p25_leverage,p50_leverage, p75_leverage, std_leverage,max_leverage,min_leverage)%<-%stats(Leverage)

c(count_profitability,mean_profitability,p25_profitability,p50_profitability, p75_profitability, std_profitability,max_profitability,min_profitability)%<-%stats(Profitability)

#Plotting the box plots for the same
plot_all_boxplots(Liquidity_Solvency)
plot_all_boxplots(Activity)
plot_all_boxplots(Asset_Utilization)
plot_all_boxplots(Leverage)
plot_all_boxplots(Profitability)

```

##NBER Recession Data
```{r}
"Loading the NBER Recession Data from FRED and merging with our dataframe"
recession_years = "USREC" %>% 
  tq_get(get = "economic.data", from = "1950-01-01") %>% 
  select(date, recession_flag = price) %>% 
  mutate(fyear = case_when(recession_flag == 1 & lag(recession_flag == 0) ~ str_glue("{year(date)}"), 
         TRUE ~ NA_character_),fyear = as.numeric(fyear)) %>%
  filter(recession_flag == 1) %>% 
  fill(fyear, .direction = "down") %>% 
  group_by(fyear) %>% 
  mutate(start = case_when(date == min(date) ~ date,
                           TRUE ~ NA_Date_),
         end = case_when(date == max(date) ~ date,
                         TRUE ~ NA_Date_),
         end = lead(end)
         ) %>% 
  filter(!is.na(start)) %>% 
  select(-c(date,start,end))
#Attaching the data with our dataframe for recession and non-recession years
all_years = seq(1950, 2020, by=1)
all_years = data.frame(fyear = all_years)
recession_years = merge(all_years,recession_years,by = "fyear",all.x = TRUE)
recession_years[is.na(recession_years)] = 0
#Adding the years 1974 and 1982 to the recession years as in these years recession continued from the previous years
recession_years[(recession_years$fyear == 1974) | (recession_years$fyear == 1982),"recession_flag"] = 1


Recession_Df = merge(Financial_Ratios_Data,recession_years[recession_years$recession_flag == 1,],by = "fyear")
Non_Recession_Df = merge(Financial_Ratios_Data,recession_years[recession_years$recession_flag == 0,],by = "fyear")

#Calculating the descriptive stats for the Recession and Non-Recession years
c(count_rescession,mean_recession,p25_recession,p50_recession,p75_recession,std_recession,max_recession,min_recession) %<-% stats(Recession_Df[c(1,87:(ncol(Recession_Df)-1))])

c(count_not_rescession,mean_not_recession,p25_not_recession,p50_not_recession,p75_not_recession,std_not_recession,max_not_recession,min_not_recession) %<-% stats(Non_Recession_Df[c(1,87:(ncol(Non_Recession_Df)-1))])

```

##Macroeconomic Data Analysis (BAA Spread, Kansas Stress Index)
```{r}
"Extracting data from FRED for the BAA spread and Kansas Stress Index for the time period and merging with the timeframe - Plotting the line charts with dual y-axis"
#Get macroeconomic data which is used for all the parts
baa_spread <- 
   "BAAFFM" %>% 
  tq_get(get = "economic.data", from = "1950-01-01") %>% 
  select(fyear = date, spread  =  price) %>% 
  mutate(fyear = as.numeric(year(fyear)))%>%
  group_by(fyear)%>%
  slice(n())

kansas_stress_index<- 
  "KCFSI" %>% 
  tq_get(get = "economic.data", from = "1950-01-01") %>% 
  select(fyear = date, ksi = price) %>% 
  mutate(fyear = as.numeric(year(fyear)))%>%
  group_by(fyear)%>%
  slice(n())

BAA_Df = merge(mean_key_variables_t9,baa_spread,by = "fyear")

Stress_Df =  merge(mean_key_variables_t9,kansas_stress_index,by = "fyear")

plot_multiple_line_chart(BAA_Df,"Financial Variables","Ratio",1)
plot_multiple_line_chart(Stress_Df,"Financial Variables","Ratio",1)

```

##1992 Dollars Terms Analysis for Table 9 
```{r}
"Creating and using old varibales in previous tables to create new variables for Table 9 descriptive stats and Box plots"
Dollar_Terms_t9 = Modified_Data %>% 
  mutate(at = at,
         sale = sale,
         book_value_debt = dlc+dltt,
         dv = dv,
         capital_investments = investment_net_assets*(at-lct),
         change_working_capital = change_working_capital_net_assets*(at-lct),
         internal_cash_flow = internal_cash_flow_net_assets*(at-lct),
         financing_deficit = financing_deficit_net_assets*(at-lct),
         long_term_debt_issuance = dltis,
         reduction_long_term_debt = dltr,
         net_debt_issued = long_term_debt_issuance - reduction_long_term_debt,
         common_stock_sale = sstk,
         common_stock_purchase = prstkc,
         net_equity_issued = common_stock_sale - common_stock_purchase,
         net_external_financing = net_debt_issued + net_equity_issued)
  
#Replace NA values back for initial variables for Balance sheet, income statement and cash flow statement because we want to keep those NA values which we have replace earlier by 0 in previous operation. This is done to calcualte precisely the values of descriptive stats
Dollar_Terms_t9_NA = copy(Dollar_Terms_t9)
for (i in (1:ncol(na_values))){
  if(any(na_values[,i])){
    Dollar_Terms_t9_NA[,i] = replace(as.vector(unlist(Dollar_Terms_t9_NA[,i])), na_values[,i] == TRUE, NA)
  }
}

Dollar_Terms_t9_NA = Dollar_Terms_t9_NA %>% 
  select(fyear,at,sale,book_value_debt,dv,capital_investments,change_working_capital,internal_cash_flow,financing_deficit,long_term_debt_issuance,reduction_long_term_debt,net_debt_issued,common_stock_sale,common_stock_purchase,net_equity_issued,net_external_financing)

#Calculating the descriptive stats
c(count_dollar_T9,mean_dollar_T9,p25_dollar_T9,p50_dollar_T9, p75_dollar_T9, std_dollar_T9,max_dollar_T9,min_dollar_T9)%<-%stats(Dollar_Terms_t9_NA)

#Plot the box plots
plot_all_boxplots(Dollar_Terms_t9_NA,1)
# dev.off()
```

